Untitled

### 2024-05-08 code/draft-script.Rmd
add osm data

```{r load packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat.explore)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
library(classInt)   
library(svDialogs)
library(patchwork)
library(tidycensus)
library(SpatialAcc)
library(tmap)
census_api_key("e579639b59d671db18f7968d4fd8c0228da09e71")
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")
```

@@

philly <- st_read("/Users/emzhou/Desktop/sc-final-proj/City_Limits/City_Limits.shp") %>% st_transform('ESRI:102728')
fishnet <- 
  st_make_grid(philly,
               cellsize = 1640, # 500 meters
               square = TRUE) %>%
  .[philly] %>%            # fast way to select intersecting polygons
  st_sf() %>%
  mutate(uniqueID = 1:n())
```

@@

water <- st_read("/Users/emzhou/Desktop/sc-final-proj/Hydrographic_Features_Poly-shp (1)/dissovled.shp") %>% st_transform('ESRI:102728')
inWater <- water %>% 
  st_buffer(dist = 330) %>% 
  st_intersection(st_centroid(fishnet), .) %>% 
  st_drop_geometry() %>% 
  dplyr::select(uniqueID)

@@

evse <- read.csv("/Users/emzhou/Desktop/sc-final-proj/alt_fuel_stations (Nov 21 2023).csv")
evse <- evse %>% 
  filter(City == "Philadelphia") %>% 
  dplyr::select(Latitude, Longitude, EV.Level2.EVSE.Num) %>% 
  filter(is.na(Latitude) == FALSE & is.na(Longitude) == FALSE) %>% 
  st_as_sf(., coords = c("Longitude", "Latitude"), crs = 4326) %>% 
  st_transform('ESRI:102728') %>% 
  mutate(num = ifelse(is.na(EV.Level2.EVSE.Num), 1, EV.Level2.EVSE.Num))

@@

reg_ev <- st_read("/Users/emzhou/Desktop/sc-final-proj/zip-fueltype-bin-shp/zip-fueltype-bin.shp")

@@

parking <- st_read("/Users/emzhou/Desktop/sc-final-proj/osm_featers/parking.geojson")

@@

police_fire <- st_read("/Users/emzhou/Desktop/sc-final-proj/osm_featers/police_fire.geojson") %>% st_transform('ESRI:102728') %>% st_centroid()

@@

zoning <- st_read("/Users/emzhou/Desktop/sc-final-proj/osm_featers/zoning.geojson")

>>>>

```{r load packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(sf)
library(RSocrata)
library(viridis)
library(spatstat.explore)
library(raster)
library(spdep)
library(FNN)
library(grid)
library(gridExtra)
library(knitr)
library(kableExtra)
library(tidycensus)
library(classInt)   
library(svDialogs)
library(patchwork)
library(tidycensus)
library(SpatialAcc)
library(tmap)
library(here)
library(svDialogs)
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")
```

```{r}
census_api_key(dlgInput("Enter a Census API Key", 
  Sys.getenv("CENSUS_API_KEY"))$res,
  overwrite = TRUE)
```

@@

philly <- st_read(here("data", "raw", "city_boundary.geojson")) %>% st_transform('ESRI:102728')
fishnet <- st_make_grid(philly,
               cellsize = 1640, # 500 meters
               square = TRUE) %>%
  .[philly] %>%           
  st_sf() %>%
  mutate(uniqueID = 1:n())
```

@@

water <- st_read(here("data", "raw", "water_features.geojson")) %>% st_transform('ESRI:102728')
inWater <- water %>% 
  st_buffer(dist = 330) %>% 
  st_intersection(st_centroid(fishnet), .) %>% 
  st_drop_geometry() %>% 
  dplyr::select(uniqueID)

@@

evse <- read.csv(here("data", "raw", "existing_evse.csv"))
evse <- evse %>% 
  filter(City == "Philadelphia") %>% 
  dplyr::select(Latitude, Longitude, EV.Level2.EVSE.Num) %>% 
  filter(is.na(Latitude) == FALSE & is.na(Longitude) == FALSE) %>% 
  st_as_sf(., coords = c("Longitude", "Latitude"), crs = 4326) %>% 
  st_transform('ESRI:102728') %>% 
  mutate(num = ifelse(is.na(EV.Level2.EVSE.Num), 1, EV.Level2.EVSE.Num))

@@

reg_ev <- st_read(here("data", "raw", "reg_ev.geojson"))

@@

parking <- st_read(here("data", "raw", "osm_features", "parking.geojson"))

@@

police_fire <- st_read(here("data", "raw", "osm_features", "police_fire.geojson")) %>% st_transform('ESRI:102728') %>% st_centroid()

@@

zoning <- st_read(here("data", "raw", "osm_features", "zoning.shp"))
